\documentclass{scrreport}
\usepackage[utf8]{inputenc}

% Add any additional packages you may need here

\renewcommand*{\thesection}{\Roman{section}}
\renewcommand*{\thesubsection}{\arabic{subsection}}
\renewcommand*{\thesubsubsection}{\roman{subsubsection}}

\title{Milestone Report}
\subtitle{Open Source Integration of Hummingbot with Cardano}

\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
Hummingbot is an open-source algorithmic trading platform designed to provides traders with a comprehensive toolkit\
to automate their trading strategies across multiple centralized and decentralized cryptocurrency exchanges. Developed in Python,\
Hummingbot offers a flexible and customizable framework for traders to efficiently implement, deploy \
and execute various algorithmic trading strategies inluding sophisticated market making, arbitrage and directional strastegies.

One of the key features of Hummingbot is its abstraction of exchange and blockchain APIs\
which alows for the portability of trading strategies across venues.\
Traders can deploy their strategies across various exchanges simultaneously, thus \
maximizing their opportunities. 

The project aims to integrate Hummingbot with decentralized exchanges (DEXs) on the \
Cardano blockchain. By enableing the users of Hummingbot to deploy their strategies,\
we seek to enhance liquidity and trading efficiency within the Cardano DEX ecosystem, \
ultimately contributing to the growth and development of decentralized finance (DeFi) on \
the Cardano platform.

This milesstone report will provide an overview of the cardano DEX ecosystem and describe the selection criteria leading to the identification of Two implementation targets\dots\
Finaly, we provide a concrete implementation plan for the selected targets


\section{Cardano DEX Ecosystem}
Describe the Cardano decentralized exchange (DEX) ecosystem, including an overview of major DEXs currently operating on the Cardano blockchain.
\subsection[]{Spot DEXs}
\subsection[]{Perpetual DEXs}

\section{Selection Process}
\subsection[]{Criteria}
\subsection[]{Conclusion}

Detail the process used to select one spot DEX and one perpetual DEX for integration with Hummingbot. Include factors considered in the selection process, such as liquidity, trading volume, user base, fees, and technical features.

\section{Project Plan}
Present a detailed project plan for the following milestones, outlining tasks, timelines, dependencies, and resource allocation for integrating the selected spot DEX and perpetual DEX with Hummingbot.

\section{Conclusion}
Summarize the key findings of the milestone report and outline the next steps in the project.

\end{document}
